---
title: "Assignment B1?"
author: "Julia D"
date: "2024-10-24"
output: github_document
---
## Assignment B1
```{r}
#Installing library
library(tidyverse)
library(palmerpenguins)
library(gapminder)
library(testthat)
library(devtools)

```

### Excerise 1 & 2
Creating a function, doesn't have to be complex or serious. The function **should** be flexible. 
My idea is to create a function that will be able to group categories and calculate the mean as long as it is a _numeric variable_
Documenting a function, using roxygen2 tags

```{r}
#'Grouped Means
#'@description
#'This is a function that groups by a variable and calculates the mean
#'@param Data Data is the dataframe 
#'@param group_var is the grouping variable you want to group by
#'@param mean_var is the column you want the means for 
#'@details This function will return an error for any non-numeric variables in the mean_var param. This function will automatically remove NA variables
#'@returns This function returns a tibble with two columns of the catgeories grouped by and the means for each 
#'@examples for palmer penguins dataset: group_mean(penguins, species, bill_length_mm), returns mean bill length by species.


group_mean <-function(data, group_var, mean_var) {
  if(!is.numeric(data[[deparse(substitute(mean_var))]])) {
    stop('Sorry, this function requires a numeric variable')
    }
  data %>%
    group_by({{group_var}}) %>%
     summarise(mean = mean({{mean_var}}, na.rm = TRUE))
  }

```

### Excerise 3
#### Examples of how this function may be used
Example 1: 
```{r}
#Finding the average bill length by species in the penguins dataset
answer1.0 <-group_mean(penguins, species, bill_length_mm)
print(answer1.0)

```
Example 2: 
```{r}
#Finding the average life expectancy by country in the gapminder dataset
answer2.0 <-group_mean(gapminder, country, lifeExp)
print(answer2.0)

```
Example3
```{r}
#Finding the average GDP per capita by continent in the gapminder dataset
answer3.0 <-group_mean(gapminder, continent, gdpPercap)
print(answer3.0)

```

### Excerise 4
Testing the function 
```{r}
#I want to test that the function is running as expected and does not conduct an analysis on non-numeric variables. 
group_mean <-function(data, group_var, mean_var) {
  if(!is.numeric(data[[deparse(substitute(mean_var))]])) {
    stop('Sorry, this function requires a numeric variable')
    }
  data %>%
    group_by({{group_var}}) %>%
     summarise(mean = mean({{mean_var}}, na.rm = TRUE))
  }

test_that("Testing group_mean function", {
  expect_type(group_mean, "closure")
  expect_error(group_mean(data, group_var, (!is.numeric(data[[deparse(substitute(mean_var))]]))))
  expect_visible(group_mean)
 
})

```



